Elders stove grades and usage summary

### 2020-06-09 indoor_temp_rh_cleaning.Rmd
update file paths

# Load, format, and save indoor temp/rh data for NP
```{r}
## Box location: Update Box location once final data loaded
np_temp_rh_initial <- read_csv("Input/NP/np_qtrack_20200214.csv") %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         rh_indoor_current = as.numeric(RelHumCur),
         rh_indoor_max = as.numeric(RelHumMax),
         rh_indoor_min = as.numeric(RelHumMin),
         temp_indoor_current = as.numeric(TempCCur),
         temp_indoor_max = as.numeric(TempCMax),
         temp_indoor_min = as.numeric(TempCMin),
         sampling_visit = as.factor(SamplingVisit),
         area = "NP") %>% 
  # replace -999 and 0 values with NA
  replace_with_na(replace = list(rh_indoor_current = -999, rh_indoor_max = -999,
                                 rh_indoor_min = -999, temp_indoor_current = -999,
                                 temp_indoor_max = -999, temp_indoor_min = -999)) %>% 
  replace_with_na(replace = list(rh_indoor_current = 0, rh_indoor_max = 0,
                                 rh_indoor_min = 0, temp_indoor_current = 0,
                                 temp_indoor_max = 0, temp_indoor_min = 0)) %>% 
  select(home_winter_id, area, rh_indoor_current, 
         rh_indoor_max, rh_indoor_min, temp_indoor_current, 
         temp_indoor_max, temp_indoor_min, sampling_visit) %>% 
  arrange(home_winter_id)
#write_rds(np_temp_rh_initial, "Output/np_temp_rh.rds")
```

# Load, format, and save indoor temp/rh data for NN
```{r}

```

# Join temp/rh data from different areas
```{r}
np_temp_rh <- read_rds("Output/np_temp_rh.rds")
nn_temp_rh <- read_rds("Output/nn_temp_rh.rds")
adult_indoor_temp_rh <- rbind(np_temp_rh, nn_temp_rh)
# write_rds(adult_indoor_temp_rh, "Output/adult_indoor_temp_rh.rds")
```

# Clean up all temp/rh data
```{r}
adult_indoor_temp_rh <- read_rds("Output/adult_indoor_temp_rh.rds")

kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
indoor_temp_rh_clean <- kids_indoor_temp_rh %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))
# write_rds(indoor_temp_rh_clean, "Output/indoor_temp_rh_clean.rds")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")
```

# Load, format, and save indoor temp/rh data
```{r}
## Box location: Update Box location once final data loaded
np_temp_rh_initial <- read_xlsx(paste0(file_path, "Input/NP/np_qtrack_20200225.xlsx")) %>% 
  # rename variables
  mutate(home_winter_id = factor(HomeWinterID),
         rh_indoor_current = as.numeric(RelHumCur),
         rh_indoor_max = as.numeric(RelHumMax),
         rh_indoor_min = as.numeric(RelHumMin),
         temp_indoor_current = as.numeric(TempCCur),
         temp_indoor_max = as.numeric(TempCMax),
         temp_indoor_min = as.numeric(TempCMin),
         sampling_visit = factor(SamplingVisit),
         area = "NP") %>% 
  # replace -999 and 0 values with NA
  replace_with_na(replace = list(rh_indoor_current = -999, rh_indoor_max = -999,
                                 rh_indoor_min = -999, temp_indoor_current = -999,
                                 temp_indoor_max = -999, temp_indoor_min = -999)) %>% 
  replace_with_na(replace = list(rh_indoor_current = 0, rh_indoor_max = 0,
                                 rh_indoor_min = 0, temp_indoor_current = 0,
                                 temp_indoor_max = 0, temp_indoor_min = 0)) %>% 
  select(home_winter_id, area, rh_indoor_current, 
         rh_indoor_max, rh_indoor_min, temp_indoor_current, 
         temp_indoor_max, temp_indoor_min, sampling_visit) %>% 
  arrange(home_winter_id)

## Box location: Update Box location once final data loaded
nn_temp_rh_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_qtrack_20200225.xlsx")) %>% 
  # rename variables
  mutate(home_winter_id = factor(HomeWinterID),
         rh_indoor_current = as.numeric(RelHumCur),
         rh_indoor_max = as.numeric(RelHumMax),
         rh_indoor_min = as.numeric(RelHumMin),
         temp_indoor_current = as.numeric(TempCCur),
         temp_indoor_max = as.numeric(TempCMax),
         temp_indoor_min = as.numeric(TempCMin),
         sampling_visit = factor(SamplingVisit),
         area = "NN") %>% 
  # replace -999 and 0 values with NA
  replace_with_na(replace = list(rh_indoor_current = -999, rh_indoor_max = -999,
                                 rh_indoor_min = -999, temp_indoor_current = -999,
                                 temp_indoor_max = -999, temp_indoor_min = -999)) %>% 
  replace_with_na(replace = list(rh_indoor_current = 0, rh_indoor_max = 0,
                                 rh_indoor_min = 0, temp_indoor_current = 0,
                                 temp_indoor_max = 0, temp_indoor_min = 0)) %>% 
  select(home_winter_id, area, rh_indoor_current, 
         rh_indoor_max, rh_indoor_min, temp_indoor_current, 
         temp_indoor_max, temp_indoor_min, sampling_visit) %>% 
  arrange(home_winter_id)

# Combine locations and save
elders_temp_rh <- rbind(np_temp_rh_initial, nn_temp_rh_initial)

#write_rds(elders_temp_rh, paste0(file_path, "Output/elders_temp_rh.rds"))
```

# Clean up all temp/rh data
```{r}
elders_temp_rh <- read_rds(paste0(file_path, "Output/elders_temp_rh.rds"))

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))

elders_temp_rh_clean <- elders_temp_rh %>% 
  left_join(elders_ids_linked, by = c("area", "home_winter_id")) %>% 
  filter(!is.na(home_winter_id))
# write_rds(elders_temp_rh_clean, paste0(file_path, "Output/elders_temp_rh_clean.rds"))

elders_temp_rh_clean <- read_rds(paste0(file_path, "Output/elders_temp_rh_clean.rds"))
```

### 2020-06-09 indoor_temp_rh_summary.Rmd
update file paths

```{r}
# Load data
indoor_temp_rh_clean <- read_rds("Output/elders_temp_rh_clean.rds")
elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

# Load data
indoor_temp_rh_clean <- read_rds(paste0(file_path, "Output/elders_temp_rh_clean.rds"))
elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))
```

### 2020-06-09 medvisit_data_cleaning.Rmd
update health summary data
update file paths

---
title: "EldersAIR initial PM data work"
author: "Ethan Walker"
date: "Started 20 Feb 2020, Updated 24 Feb 2020"
output: pdf_document
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds") %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  arrange(area, adult_id_num)
```

# Initial load, format, save medical visit data
```{r}
## Box location: Update Box location once final data loaded
np_medvisit_initial <- read_xlsx("Input/NP/np_medicalvisit_20200220.xlsx")

@@

## Box location: Update Box location once final data loaded
nn_medvisit_initial <- read_xlsx("Input/NN/nn_medicalvisit_20200220.xlsx")

@@

write_csv(save_var_names, "Output/medvisit_var_names.csv")
```

# Summary stats to help with further data cleaning
```{r}
elders_medvisit <- read_rds("Output/elders_medvisit_clean.rds") %>% 
  mutate(hypertension = if_else(bp_sys >= 140 | bp_dia >= 90, 1, 0),
         hypertension = as.numeric(hypertension),
         obstruction = if_else(fev1_fvc_ratio < 0.7 | fev1_pp < 75, 1, 0),
         obstruction = as.numeric(obstruction))

>>>>

---
title: "EldersAIR initial med visit data work"
author: "Ethan Walker"
date: "Started 20 Feb 2020, Updated 24 Feb 2020"
output: pdf_document
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds")) %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  arrange(area, adult_id_num)
```

# Initial load, format, save medical visit data
```{r}
## Box location: Update Box location once final data loaded
np_medvisit_initial <- read_xlsx(paste0(file_path, "Input/NP/np_medicalvisit_20200220.xlsx"))

@@

## Box location: Update Box location once final data loaded
nn_medvisit_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_medicalvisit_20200220.xlsx"))

@@

write_csv(save_var_names, paste0(file_path, "Output/medvisit_var_names.csv"))
```

# Summary stats to help with further data cleaning
```{r}
elders_medvisit <- read_rds(paste0(file_path, "Output/elders_medvisit_clean.rds")) %>% 
  mutate(hypertension = if_else(bp_sys >= 140 | bp_dia >= 90, 1, 0),
         hypertension = as.numeric(hypertension),
         obstruction = if_else(fev1_fvc_ratio < 0.7 | fev1_pp < 75, 1, 0),
         obstruction = as.numeric(obstruction))

### 2020-06-09 medvisit_summary.Rmd
update file paths

```{r}
# Load data

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds") %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  arrange(area, adult_id_num)

elders_medvisit <- read_rds("Output/elders_medvisit_clean.rds") %>% 
  mutate(hypertension = if_else(bp_sys >= 140 | bp_dia >= 90, 1, 0),
         hypertension = as.numeric(hypertension),
         obstruction = if_else(fev1_fvc_ratio < 0.7 | fev1_pp < 75, 1, 0),
         obstruction = as.numeric(obstruction))
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

# Load data

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds")) %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  arrange(area, adult_id_num)

elders_medvisit <- read_rds(paste0(file_path, "Output/elders_medvisit_clean.rds")) %>% 
  mutate(hypertension = if_else(bp_sys >= 140 | bp_dia >= 90, 1, 0),
         hypertension = as.numeric(hypertension),
         obstruction = if_else(fev1_fvc_ratio < 0.7 | fev1_pp < 75, 1, 0),
         obstruction = as.numeric(obstruction))
```

### 2020-06-09 micropem_data_cleaning.Rmd
update file paths

# Load, format, and save micropem log files
```{r}
## Box location: Update Box location once final data loaded
np_micropem_initial <- read_xlsx("Input/NP/np_micropem_20200225.xlsx") %>% 
  # rename variables
  separate(StartTime, c("trash1", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  separate(StopTime, c("trash1", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         home_id = as.character(HomeID),
         mpid = MicroPEMID,
         start_date_pm = ymd(StartDate),
         start_time_pm = as.character(start_time_pm),
         stop_date_pm = ymd(StopDate),
         stop_time_pm = as.character(stop_time_pm),
         sample_obs = as.numeric(LengthofRun),
         file_name = as.character(mFile),
         sampling_visit = as.factor(SamplingVisit),
         area = "NP") %>% 
  separate(file_name, c("trash1", "file_name"), sep = "uploads/", remove = FALSE) %>% 
  separate(file_name, c("file_name", "trash1"), sep = ".csv", remove = FALSE) %>%
  separate(file_name, c("file_name", "trash1"), sep = ".xlsx", remove = FALSE) %>%
  select(home_winter_id, home_id, area, mpid, sampling_visit, 
         start_date_pm, start_time_pm, stop_date_pm, stop_time_pm, sample_obs, 
         file_name) %>% 
  arrange(home_winter_id)
#write_rds(np_micropem_initial, "Output/np_micropem_log.rds")

## Box location: Update Box location once final data loaded
nn_micropem_initial <- read_xlsx("Input/NN/nn_micropem_20200225.xlsx") %>% 
  # rename variables
  separate(StartTime, c("trash1", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  separate(StopTime, c("trash1", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         home_id = as.character(HomeID),
         mpid = MicroPEMID,
         start_date_pm = ymd(StartDate),
         start_time_pm = as.character(start_time_pm),
         stop_date_pm = ymd(StopDate),
         stop_time_pm = as.character(stop_time_pm),
         sample_obs = as.numeric(LengthofRun),
         file_name = as.character(mFile),
         sampling_visit = as.factor(SamplingVisit),
         area = "NN") %>% 
  separate(file_name, c("trash1", "file_name"), sep = "uploads/", remove = FALSE) %>% 
  separate(file_name, c("file_name", "trash1"), sep = ".csv", remove = FALSE) %>%
  separate(file_name, c("file_name", "trash1"), sep = ".xlsx", remove = FALSE) %>%
  select(home_winter_id, home_id, area, mpid, sampling_visit, 
         start_date_pm, start_time_pm, stop_date_pm, stop_time_pm, sample_obs, 
         file_name) %>% 
  arrange(home_winter_id)
#write_rds(nn_micropem_initial, "Output/nn_micropem_log.rds")

elders_micropem_log <- rbind(np_micropem_initial, nn_micropem_initial)
#write_rds(elders_dustrak_log, "Output/elders_dustrak_log.rds")

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds") %>% 
  filter(winter_id == 1 | winter_id == 2)

elders_micropem_log_new <- elders_micropem_log %>% 
  left_join(elders_ids_linked, by = c("area", "home_id", "home_winter_id")) %>% 
  filter(!is.na(file_name)) %>% 
  unite(start_datetime_pm, c("start_date_pm", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  unite(stop_datetime_pm, c("stop_date_pm", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  arrange(home, winter_id)
#write_rds(elders_micropem_log_new, "Output/elders_micropem_log.rds")
```

@@

### NP ###
# List files
list_files <- list.files("Input/NP/np_micropem_20200302")

# Set working directory and load files in list; extract file name and add as column
## run next lines together
setwd("Input/NP/np_micropem_20200302") # set new working directory
initial_data <- tibble(list_files) %>% # use list of files from above
  mutate(save_data = lapply(list_files, read_xlsx, range = "A29:N20000",
                            col_names = c("date", "time", "pm",
                                          "temp", "rh", "battery",
                                          "in_pressure", "or_pressure",
                                          "flow", "x_axis", "y_axis",
                                          "z_axis", "vector_sum", "shutdown_reason"),
                            col_types = c("date", "date", "numeric",
                                          "numeric", "numeric", "numeric",
                                          "numeric", "numeric",
                                          "numeric", "numeric", "numeric",
                                          "numeric", "numeric", "text"))) %>%
  unnest(save_data)

@@

# save files
#write_rds(np_micropem, "Output/np_micropem.rds")

### NN ###
# List files
list_files <- list.files("Input/NN/nn_micropem_small_20200302")

# Set working directory and load files in list; extract file name and add as column
## run next lines together
setwd("Input/NN/nn_micropem_small_20200302") # set new working directory
initial_data <- tibble(list_files) %>% # use list of files from above
  mutate(save_data = lapply(list_files, read_csv, skip = 28,
                            col_names = c("date", "time", "pm", "pm2",
                                          "temp", "rh", "battery",
                                          "in_pressure", "or_pressure",
                                          "flow", "x_axis", "y_axis",
                                          "z_axis", "vector_sum", "shutdown_reason",
                                          "trash1", "trash2"),
                            col_types = list(col_character(), col_character(), col_double(),
                                          col_double(), col_double(), col_double(),
                                          col_double(), col_double(), col_double(),
                                          col_double(), col_double(), col_double(),
                                          col_double(), col_double(), col_character(),
                                          col_character(), col_character()))) %>%
  unnest(save_data)

list_files <- list.files("Input/NN/nn_micropem_large_20200302")

# Set working directory and load files in list; extract file name and add as column
## run next lines together
setwd("Input/NN/nn_micropem_large_20200302") # set new working directory
initial_data2 <- tibble(list_files) %>% # use list of files from above
  mutate(save_data = lapply(list_files, read_csv, skip = 28,
                            col_names = c("date", "time", "pm", "pm2",
                                          "temp", "rh", "battery",
                                          "in_pressure", "or_pressure",
                                          "flow", "x_axis", "y_axis",
                                          "z_axis", "vector_sum", "shutdown_reason",
                                          "trash1", "trash2"),
                            col_types = list(col_character(), col_character(), col_double(),
                                          col_double(), col_double(), col_double(),
                                          col_double(), col_double(), col_double(),
                                          col_double(), col_double(), col_double(),
                                          col_double(), col_double(), col_character(),
                                          col_character(), col_character()))) %>%
  unnest(save_data)

@@

# Save file
#write_rds(nn_micropem, "Output/nn_micropem.rds")

@@

# save joined file
#write_rds(elders_micropem, "Output/elders_micropem.rds")
```

# Clean up and filter all micropem data
```{r}
# load data
elders_micropem_log <- read_rds("Output/elders_micropem_log.rds") %>% 
  select(home, adult_id_num, adult_id_char, home_winter_id:winter_id, 
         -sample_obs, treatment)
elders_micropem <- read_rds("Output/elders_micropem.rds")

@@

# Save data
#write_rds(nn_micropem_new2, "Output/nn_micropem_new.rds")

@@

# Save data
#write_rds(np_micropem_new2, "Output/np_micropem_new.rds")

@@

# Save data
#write_rds(elders_micropem_new, "Output/elders_micropem_new.rds")
```

# Summarize filtered micropem data for further cleaning
```{r}
elders_micropem <- read_rds("Output/elders_micropem_new.rds")

@@

# Continue micropem cleaning
```{r}
elders_micropem <- read_rds("Output/elders_micropem_new.rds")

elders_micropem_new2 <- elders_micropem %>%   
  group_by(area, file_name) %>% 
  # new variables summarizing pm2.5 within each home
  mutate(pm_total_observations = n(),
         # new datetime values to calculate sampling interval
         first_datetime = first(datetime_pm),
         last_datetime = last(datetime_pm),
         first_datetime = ymd_hms(first_datetime),
         last_datetime = ymd_hms(last_datetime),
         diff_datetime = interval(first_datetime, last_datetime),
         # total sampling interval, based on first and last datetimes
         pm_sample_interval = diff_datetime/86400,
         # expected number of observations with the sampling interval
         expected_obs = pm_sample_interval*24*60,
         # difference between actual and expected observations
         actual_vs_expected_diff = pm_total_observations - expected_obs,
         # indicator variable if actual vs expected obs > 10 or greater
         actual_vs_expected = if_else(actual_vs_expected_diff < 10 &
                                      actual_vs_expected_diff > -10, 1, 0),
         pm_mean = mean(pm_personal),
         # breaking sampling period into days
         obs = row_number(),
         sampling_day = if_else(obs < 1441, 1, 0),
         sampling_day = if_else(obs < 2881 & obs > 1440, 2, sampling_day),
         sampling_day = if_else(obs < 4321 & obs > 2880, 3, sampling_day)) %>%
  # calculate pm means for each sampling day
  group_by(area, file_name, sampling_day) %>% 
  mutate(pm_mean_daily = mean(pm_personal),
         pm_sampling_day = sampling_day,
         day_of_week = weekdays(date_pm)) %>%
  mutate(start_datetime_pm = ymd_hms(start_datetime_pm),
         pm_start_diff = interval(first_datetime, start_datetime_pm),
         pm_start_diff_hrs = pm_start_diff/3600) %>% 
  ungroup() %>% 
  select(-obs, -sampling_day) %>% 
  arrange(area, home, sampling_visit) 
# write_rds(elders_micropem_new2, "Output/elders_micropem_new2.rds")
```

@@

# Run function from above to look at results
## Function run for each household to check for odd trends/gaps in the data
## Notes from this process on uploaded to Box:
### EldersAIR > Ethan - data cleaning and analysis > pm_cleaning_summary
```{r}
# load data
elders_micropem <- read_rds("Output/elders_micropem_new2.rds")

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")
```

# Load, format, and save micropem log files
```{r}
## Box location: Update Box location once final data loaded
np_micropem_initial <- read_xlsx(paste0(file_path, "Input/NP/np_micropem_20200225.xlsx")) %>% 
  # rename variables
  separate(StartTime, c("trash1", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  separate(StopTime, c("trash1", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         home_id = as.character(HomeID),
         mpid = MicroPEMID,
         start_date_pm = ymd(StartDate),
         start_time_pm = as.character(start_time_pm),
         stop_date_pm = ymd(StopDate),
         stop_time_pm = as.character(stop_time_pm),
         sample_obs = as.numeric(LengthofRun),
         file_name = as.character(mFile),
         sampling_visit = as.factor(SamplingVisit),
         area = "NP") %>% 
  separate(file_name, c("trash1", "file_name"), sep = "uploads/", remove = FALSE) %>% 
  separate(file_name, c("file_name", "trash1"), sep = ".csv", remove = FALSE) %>%
  separate(file_name, c("file_name", "trash1"), sep = ".xlsx", remove = FALSE) %>%
  select(home_winter_id, home_id, area, mpid, sampling_visit, 
         start_date_pm, start_time_pm, stop_date_pm, stop_time_pm, sample_obs, 
         file_name) %>% 
  arrange(home_winter_id)
#write_rds(np_micropem_initial, paste0(file_path, "Output/np_micropem_log.rds"))

## Box location: Update Box location once final data loaded
nn_micropem_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_micropem_20200225.xlsx")) %>% 
  # rename variables
  separate(StartTime, c("trash1", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  separate(StopTime, c("trash1", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         home_id = as.character(HomeID),
         mpid = MicroPEMID,
         start_date_pm = ymd(StartDate),
         start_time_pm = as.character(start_time_pm),
         stop_date_pm = ymd(StopDate),
         stop_time_pm = as.character(stop_time_pm),
         sample_obs = as.numeric(LengthofRun),
         file_name = as.character(mFile),
         sampling_visit = as.factor(SamplingVisit),
         area = "NN") %>% 
  separate(file_name, c("trash1", "file_name"), sep = "uploads/", remove = FALSE) %>% 
  separate(file_name, c("file_name", "trash1"), sep = ".csv", remove = FALSE) %>%
  separate(file_name, c("file_name", "trash1"), sep = ".xlsx", remove = FALSE) %>%
  select(home_winter_id, home_id, area, mpid, sampling_visit, 
         start_date_pm, start_time_pm, stop_date_pm, stop_time_pm, sample_obs, 
         file_name) %>% 
  arrange(home_winter_id)
#write_rds(nn_micropem_initial, paste0(file_path, "Output/nn_micropem_log.rds"))

elders_micropem_log <- rbind(np_micropem_initial, nn_micropem_initial)
#write_rds(elders_dustrak_log, paste0(file_path, "Output/elders_dustrak_log.rds"))

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds")) %>% 
  filter(winter_id == 1 | winter_id == 2)

elders_micropem_log_new <- elders_micropem_log %>% 
  left_join(elders_ids_linked, by = c("area", "home_id", "home_winter_id")) %>% 
  filter(!is.na(file_name)) %>% 
  unite(start_datetime_pm, c("start_date_pm", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  unite(stop_datetime_pm, c("stop_date_pm", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  arrange(home, winter_id)
#write_rds(elders_micropem_log_new, paste0(file_path, "Output/elders_micropem_log.rds"))
```

@@

### NP ###
# List files
list_files <- list.files(paste0(file_path, "Input/NP/np_micropem_20200302"))

# Set working directory and load files in list; extract file name and add as column
## run next lines together
setwd(paste0(file_path, "Input/NP/np_micropem_20200302")) # set new working directory
initial_data <- tibble(list_files) %>% # use list of files from above
  mutate(save_data = lapply(list_files, read_xlsx, range = "A29:N20000",
                            col_names = c("date", "time", "pm",
                                          "temp", "rh", "battery",
                                          "in_pressure", "or_pressure",
                                          "flow", "x_axis", "y_axis",
                                          "z_axis", "vector_sum", "shutdown_reason"),
                            col_types = c("date", "date", "numeric",
                                          "numeric", "numeric", "numeric",
                                          "numeric", "numeric",
                                          "numeric", "numeric", "numeric",
                                          "numeric", "numeric", "text"))) %>%
  unnest(save_data)

@@

# save files
#write_rds(np_micropem, paste0(file_path, "Output/np_micropem.rds"))

### NN ###
# List files
list_files <- list.files(paste0(file_path, "Input/NN/nn_micropem_small_20200302"))

# Set working directory and load files in list; extract file name and add as column
## run next lines together
setwd(paste0(file_path, "Input/NN/nn_micropem_small_20200302")) # set new working directory
initial_data <- tibble(list_files) %>% # use list of files from above
  mutate(save_data = lapply(list_files, read_csv, skip = 28,
                            col_names = c("date", "time", "pm", "pm2",
                                          "temp", "rh", "battery",
                                          "in_pressure", "or_pressure",
                                          "flow", "x_axis", "y_axis",
                                          "z_axis", "vector_sum", "shutdown_reason",
                                          "trash1", "trash2"),
                            col_types = list(col_character(), col_character(), col_double(),
                                          col_double(), col_double(), col_double(),
                                          col_double(), col_double(), col_double(),
                                          col_double(), col_double(), col_double(),
                                          col_double(), col_double(), col_character(),
                                          col_character(), col_character()))) %>%
  unnest(save_data)

list_files <- list.files(paste0(file_path, "Input/NN/nn_micropem_large_20200302"))

# Set working directory and load files in list; extract file name and add as column
## run next lines together
setwd(paste0(file_path, "Input/NN/nn_micropem_large_20200302")) # set new working directory
initial_data2 <- tibble(list_files) %>% # use list of files from above
  mutate(save_data = lapply(list_files, read_csv, skip = 28,
                            col_names = c("date", "time", "pm", "pm2",
                                          "temp", "rh", "battery",
                                          "in_pressure", "or_pressure",
                                          "flow", "x_axis", "y_axis",
                                          "z_axis", "vector_sum", "shutdown_reason",
                                          "trash1", "trash2"),
                            col_types = list(col_character(), col_character(), col_double(),
                                          col_double(), col_double(), col_double(),
                                          col_double(), col_double(), col_double(),
                                          col_double(), col_double(), col_double(),
                                          col_double(), col_double(), col_character(),
                                          col_character(), col_character()))) %>%
  unnest(save_data)

@@

# Save file
#write_rds(nn_micropem, paste0(file_path, "Output/nn_micropem.rds"))

@@

# save joined file
#write_rds(elders_micropem, paste0(file_path, "Output/elders_micropem.rds"))
```

# Clean up and filter all micropem data
```{r}
# load data
elders_micropem_log <- read_rds(paste0(file_path, "Output/elders_micropem_log.rds")) %>% 
  select(home, adult_id_num, adult_id_char, home_winter_id:winter_id, 
         -sample_obs, treatment)
elders_micropem <- read_rds(paste0(file_path, "Output/elders_micropem.rds"))

@@

# Save data
#write_rds(nn_micropem_new2, paste0(file_path, "Output/nn_micropem_new.rds"))

@@

# Save data
#write_rds(np_micropem_new2, paste0(file_path, "Output/np_micropem_new.rds"))

@@

# Save data
#write_rds(elders_micropem_new, paste0(file_path, "Output/elders_micropem_new.rds"))
```

# Summarize filtered micropem data for further cleaning
```{r}
elders_micropem <- read_rds(paste0(file_path, "Output/elders_micropem_new.rds"))

@@

# Continue micropem cleaning
```{r}
elders_micropem <- read_rds(paste0(file_path, "Output/elders_micropem_new.rds"))

elders_micropem_new2 <- elders_micropem %>%   
  group_by(area, file_name) %>% 
  # new variables summarizing pm2.5 within each home
  mutate(pm_total_observations = n(),
         # new datetime values to calculate sampling interval
         first_datetime = first(datetime_pm),
         last_datetime = last(datetime_pm),
         first_datetime = ymd_hms(first_datetime),
         last_datetime = ymd_hms(last_datetime),
         diff_datetime = interval(first_datetime, last_datetime),
         # total sampling interval, based on first and last datetimes
         pm_sample_interval = diff_datetime/86400,
         # expected number of observations with the sampling interval
         expected_obs = pm_sample_interval*24*60,
         # difference between actual and expected observations
         actual_vs_expected_diff = pm_total_observations - expected_obs,
         # indicator variable if actual vs expected obs > 10 or greater
         actual_vs_expected = if_else(actual_vs_expected_diff < 10 &
                                      actual_vs_expected_diff > -10, 1, 0),
         pm_mean = mean(pm_personal),
         # breaking sampling period into days
         obs = row_number(),
         sampling_day = if_else(obs < 1441, 1, 0),
         sampling_day = if_else(obs < 2881 & obs > 1440, 2, sampling_day),
         sampling_day = if_else(obs < 4321 & obs > 2880, 3, sampling_day)) %>%
  # calculate pm means for each sampling day
  group_by(area, file_name, sampling_day) %>% 
  mutate(pm_mean_daily = mean(pm_personal),
         pm_sampling_day = sampling_day,
         day_of_week = weekdays(date_pm)) %>%
  mutate(start_datetime_pm = ymd_hms(start_datetime_pm),
         pm_start_diff = interval(first_datetime, start_datetime_pm),
         pm_start_diff_hrs = pm_start_diff/3600) %>% 
  ungroup() %>% 
  select(-obs, -sampling_day) %>% 
  arrange(area, home, sampling_visit) 
# write_rds(elders_micropem_new2, paste0(file_path, "Output/elders_micropem_new2.rds"))
```

@@

# Run function from above to look at results
## Function run for each household to check for odd trends/gaps in the data
## Notes from this process on uploaded to Box:
### EldersAIR > Ethan - data cleaning and analysis > pm_cleaning_summary
```{r}
# load data
elders_micropem <- read_rds(paste0(file_path, "Output/elders_micropem_new2.rds"))

### 2020-06-09 stove_grade_usage_summary.Rmd
update file paths

```{r}
# Load data
stove_grades_clean <- read_rds("Output/elders_stove_grades_clean.rds")
stove_use_clean <- read_rds("Output/elders_stove_usage_clean.rds")
elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")
elders_pm <- read_rds("Output/elders_pm_clean.rds")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

# Load data
stove_grades_clean <- read_rds(paste0(file_path, "Output/elders_stove_grades_clean.rds"))
stove_use_clean <- read_rds(paste0(file_path, "Output/elders_stove_usage_clean.rds"))
elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))
elders_pm <- read_rds(paste0(file_path, "Output/elders_pm_clean.rds"))
```
